### 2019-03-06 ic-journal/formal.tex
Clean up the rest DDS macros; disable line numbers

\emph{In this
formalisation we consider only single-variable equations/contractions.}
This considerably
 simplifies the required proofs in HOL, and  enhances the readability of
 proof scripts without loss of generality. For the  pencil-and-paper proofs, the
 multi-variable case is just a routine adaptation, while the   formalisation
 is not (this is also discussed in Section~\ref{s:concl}).

>>>>

\emph{In this
formalisation we consider only single-variable equations/contractions.}
This considerably
 simplifies the required proofs in HOL, and  enhances the readability of
 proof scripts without loss of generality. For the  pencil-and-paper proofs, the
 multi-variable case is just a routine adaptation, while the
 formalisation in theorem prover % \DDS{}
 is not (this is also discussed in Section~\ref{s:concl}).
